---
    output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    collapse=TRUE,
    comment="#>",
    fig.path="man/figures/README-",
    fig.height = 7,
    out.width="100%"
)
```



# crosstable
<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/crosstableAssistant)](https://CRAN.R-project.org/package=crosstable)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)

Crosstable is a package centered on a single function, `crosstable`, which easily computes descriptive statistics on datasets. You can learn about it on its [dedicated page](https://github.com/DanChaltiel/crosstable).

CrosstableAssistant is an RShiny application, designed as an RStudio addin, which makes the use of `crosstable` much easier by providing a graphical interface for all its parameters.

## Installation

```{r install, eval=FALSE}
install.packages("devtools")
devtools::install_github("DanChaltiel/crosstable")
devtools::install_github("DanChaltiel/crosstableAssistant")
```

## Usage

```{r usage0, eval=FALSE}
library(crosstable)

my_dataset = crosstable::mtcars2
crosstableAssistant(my_dataset)
```

Alternatively, if you are using RStudio, you can use the "Crosstable Assistant" addin. Just select your dataset in the "source" panel and it will be loaded inside the assistant.

## Acknowledgement

This `crosstableAssistant` package is highly inspired by `dreamRs`' amazing addin `esquisse` ([link](https://github.com/dreamRs/esquisse)), which is designed to easily build plots with ggplot2. If you never did, you should definitely give it a try.

Thanks `dreamRs`!
